```{r}
# source functions
source('ColorPaletteGeneration.R')

```
Bank History {data-icon="fa-search"}
=====================================


```{r}

###################################################################
#### This chunk contains the CRE_Hist on the Bank Data Overview page
#### First we create conditional CRE_Hist with renderUI
#### Second we create the logic for the select all/unselect all buttons
#### Third, we create logic for the measure selection, which has to be dependent on each other
####    it consists of multiple menus but they should only allow one item to be selected across all menus
#### Fourth we render everything in a navbar
####################################################################

#### First we create conditional CRE_Hist with renderUI

output$countryFilterSettingHist1UI <- renderUI({
  checkboxGroupButtons(inputId = "countryFilterSettingHist1", 
  label = "Europe", choices = intersect(unique(results()$Country), unique(CRE_Hist[Continent=='Europe' & BankNameShort %in% input$bankFilterSettingHist, Country])), selected = 'NL', individual = TRUE, 
  checkIcon = checkIconList)
})

output$countryFilterSettingHist2UI <- renderUI({
  checkboxGroupButtons(inputId = "countryFilterSettingHist2", 
    label = "Asia", choices = intersect(unique(results()$Country), unique(CRE_Hist[Continent=='Asia' & BankNameShort %in% input$bankFilterSettingHist, Country])), individual = TRUE, 
    checkIcon = checkIconList)
})

output$countryFilterSettingHist3UI <- renderUI({
  
  checkboxGroupButtons(inputId = "countryFilterSettingHist3", 
  label = "Americas", choices = intersect(unique(results()$Country), unique(CRE_Hist[Continent=='Americas' & BankNameShort %in% input$bankFilterSettingHist, Country])), individual = TRUE, 
  checkIcon = checkIconList)
  
})

output$countryFilterSettingHist4UI <- renderUI({
  
  checkboxGroupButtons(inputId = "countryFilterSettingHist4", 
  label = "Other", choices = intersect(c('ALL', unique(results()$Country)), unique(CRE_Hist[!Continent %in% c('Americas', 'Asia', 'Europe') & BankNameShort %in% input$bankFilterSettingHist, Country])), individual = TRUE, 
  checkIcon = checkIconList)
  
})

output$ExposureTypeFilterSettingHist1UI <- renderUI({
  checkboxGroupButtons(inputId = "ExposureTypeFilterSettingHist1", 
    label = "Corporates", choices = unique(CRE_Hist[ExposureClass=='Corporates' & BankNameShort %in% input$bankFilterSettingHist & Country %in% c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4), ExposureLabel]), selected = 'Large Corporates', individual = TRUE, 
    checkIcon = checkIconList)
})

output$ExposureTypeFilterSettingHist2UI <- renderUI({
  checkboxGroupButtons(inputId = "ExposureTypeFilterSettingHist2", 
    label = "Retail", choices = unique(CRE_Hist[ExposureClass=='Retail' & BankNameShort %in% input$bankFilterSettingHist & Country %in% c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4), ExposureLabel]),  individual = TRUE, 
    checkIcon = checkIconList)
})

#### Second we create the logic for the select all/unselect all buttons

# for later reference in this second part, but also third part
checkIconList <- list(yes = tags$i(class = "fa fa-circle", 
                      style = "color: steelblue"), 
                      no = tags$i(class = "fa fa-circle-o", 
                      style = "color: steelblue"))

# Bank dropdown
observeEvent(input$selectAllBanks, {
      shinyWidgets::updateCheckboxGroupButtons(session, "bankFilterSettingHist", "Bank Setting", choices=unique(CRE_Hist$BankNameShort), selected=unique(CRE_Hist$BankNameShort), checkIcon = checkIconList)
})
observeEvent(input$deselectAllBanks, {
      shinyWidgets::updateCheckboxGroupButtons(session, "bankFilterSettingHist", "Bank Setting", choices=unique(CRE_Hist$BankNameShort), selected=NULL, checkIcon = checkIconList)
})
# Country dropdown
# Europe
observeEvent(input$selectAllEurope, {
      shinyWidgets::updateCheckboxGroupButtons(session, "countryFilterSettingHist1", "Europe", choices=countriesShortCodeContinent[Continent == 'Europe', Country][which(countriesShortCodeContinent[Continent == 'Europe', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], selected=countriesShortCodeContinent[Continent == 'Europe', Country][which(countriesShortCodeContinent[Continent == 'Europe', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], checkIcon = checkIconList)
})
observeEvent(input$deselectAllEurope, {
      shinyWidgets::updateCheckboxGroupButtons(session, "countryFilterSettingHist1", "Bank Setting", choices=countriesShortCodeContinent[Continent == 'Europe', Country][which(countriesShortCodeContinent[Continent == 'Europe', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], selected=NULL, checkIcon = checkIconList)
})
# Asia
observeEvent(input$selectAllAsia, {
      shinyWidgets::updateCheckboxGroupButtons(session, "countryFilterSettingHist2", "Asia", choices=countriesShortCodeContinent[Continent == 'Asia', Country][which(countriesShortCodeContinent[Continent == 'Asia', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], selected=countriesShortCodeContinent[Continent == 'Asia', Country][which(countriesShortCodeContinent[Continent == 'Asia', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], checkIcon = checkIconList)
})
observeEvent(input$deselectAllAsia, {
      shinyWidgets::updateCheckboxGroupButtons(session, "countryFilterSettingHist2", "Asia", choices=countriesShortCodeContinent[Continent == 'Asia', Country][which(countriesShortCodeContinent[Continent == 'Asia', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], selected=NULL, checkIcon = checkIconList)
})
# Americas
observeEvent(input$selectAllAmericas, {
      shinyWidgets::updateCheckboxGroupButtons(session, "countryFilterSettingHist3", "Americas", choices=countriesShortCodeContinent[Continent == 'Americas', Country][which(countriesShortCodeContinent[Continent == 'Americas', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], selected=countriesShortCodeContinent[Continent == 'Americas', Country][which(countriesShortCodeContinent[Continent == 'Americas', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], checkIcon = checkIconList)
})
observeEvent(input$deselectAllAmericas, {
      shinyWidgets::updateCheckboxGroupButtons(session, "countryFilterSettingHist3", "Americas", choices=countriesShortCodeContinent[Continent == 'Americas', Country][which(countriesShortCodeContinent[Continent == 'Americas', Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], selected=NULL, checkIcon = checkIconList)
})
# Other
observeEvent(input$selectAllOther, {
      shinyWidgets::updateCheckboxGroupButtons(session, "countryFilterSettingHist4", "Other", choices=unique(CRE_Hist[!Continent %in% c('Americas', 'Asia', 'Europe') & BankNameShort %in% input$bankFilterSettingHist, Country]), selected = unique(CRE_Hist[!Continent %in% c('Americas', 'Asia', 'Europe') & BankNameShort %in% input$bankFilterSettingHist, Country]), checkIcon = checkIconList)
})
observeEvent(input$deselectAllOther, {
      shinyWidgets::updateCheckboxGroupButtons(session, "countryFilterSettingHist4", "Other", choices=countriesShortCodeContinent[!Continent %in% c('Americas', 'Asia', 'Europe'), Country][which(countriesShortCodeContinent[!Continent %in% c('Americas', 'Asia', 'Europe'), Country] %in% CRE_Hist[BankNameShort %in% input$bankFilterSettingHist, Country])], selected=NULL, checkIcon = checkIconList)
})
# Exposure type dropdown
# corporates
observeEvent(input$selectAllCorporates, {
      shinyWidgets::updateCheckboxGroupButtons(session, "ExposureTypeFilterSettingHist1", "Corporates", choices=unique(CRE_Hist[ExposureClass=='Corporates' & BankNameShort %in% input$bankFilterSettingHist & Country %in% c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4), ExposureLabel]), selected=unique(CRE_Hist[ExposureClass=='Corporates' & BankNameShort %in% input$bankFilterSettingHist & Country %in% c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4), ExposureLabel]), checkIcon = checkIconList)
})
observeEvent(input$deselectAllCorporates, {
      shinyWidgets::updateCheckboxGroupButtons(session, "ExposureTypeFilterSettingHist1", "Corporates", choices=unique(CRE_Hist[ExposureClass=='Corporates' & BankNameShort %in% input$bankFilterSettingHist & Country %in% c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4), ExposureLabel]), selected=NULL, checkIcon = checkIconList)
})
# retail
observeEvent(input$selectAllRetail, {
      shinyWidgets::updateCheckboxGroupButtons(session, "ExposureTypeFilterSettingHist2", "Retail", choices=unique(CRE_Hist[ExposureClass=='Retail' & BankNameShort %in% input$bankFilterSettingHist & Country %in% c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4), ExposureLabel]), selected=unique(CRE_Hist[ExposureClass=='Retail' & BankNameShort %in% input$bankFilterSettingHist & Country %in% c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4), ExposureLabel]), checkIcon = checkIconList)
})
observeEvent(input$deselectAllRetail, {
      shinyWidgets::updateCheckboxGroupButtons(session, "ExposureTypeFilterSettingHist2", "Retail", choices=unique(CRE_Hist[ExposureClass=='Retail' & BankNameShort %in% input$bankFilterSettingHist & Country %in% c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4), ExposureLabel]), selected=NULL, checkIcon = checkIconList)
})

#### Fourth we render everything in a navbar

shinyUI(
  fluidPage(
    navbarPage("",
               tabPanel(
                 div(style="display: inline-block; align: center;",
                     shinyWidgets::dropdown(label='Bank', status = "primary",
    fluidRow(
       column(10,offset=0,
          div(style = "padding: 0px 0px; margin-left:0.1%",
checkboxGroupButtons(inputId = "bankFilterSettingHist", 
  label = "Selection of banks(s)", choices = unique(CRE_Hist$BankNameShort), selected = unique(CRE_Hist$BankNameShort),individual = TRUE, 
  checkIcon = checkIconList),
br(),
actionButton("selectAllBanks", "Select All"),
actionButton("deselectAllBanks", "Deselect All")
  ))))
  , circle = F, status = "primary",
    icon = icon("time"), width = "300px",
    tooltip = tooltipOptions(title = "Click to modify")
))  ,

  tabPanel(div(style="display: inline-block;",shinyWidgets::dropdown(label = 'Country',
    fluidRow(
        column(3,offset=0,
       div(style="display: inline-block; align: center;",
           uiOutput('countryFilterSettingHist1UI'),
           br(),
           actionButton("selectAllEurope", "Select All"),
           actionButton("deselectAllEurope", "Deselect All")
           ,
    circle = F, status = "primary",
    icon = icon("time"), width = "300px",
    tooltip = tooltipOptions(title = "Click to modify")
)
               
               ),
    
      column(3,offset=0,
       div(style = "padding: 0px 0px; margin-left:0.1%",
        uiOutput('countryFilterSettingHist2UI'),
           br(),
           actionButton("selectAllAsia", "Select All"),
           actionButton("deselectAllAsia", "Deselect All")
       )),


column(3,offset=0,
       div(style = "padding: 0px 0px; margin-left:0.1%",
           uiOutput('countryFilterSettingHist3UI'),
           br(),
           actionButton("selectAllAmericas", "Select All"),
           actionButton("deselectAllAmericas", "Deselect All")
       )),

column(3,offset=0,
       div(style = "padding: 0px 0px; margin-left:0.1%",
           uiOutput('countryFilterSettingHist4UI'),
           br(),
           actionButton("selectAllOther", "Select All"),
           actionButton("deselectAllOther", "Deselect All")
       ))

  )
  ,
    circle = F, status = "primary", width = "1000px",
    tooltip = tooltipOptions(title = "Click to modify")
  ))),

  tabPanel(div(style="display: inline-block;",shinyWidgets::dropdown(label = 'Exposure',
    fluidRow(
        column(4,offset=0,
       div(style="display: inline-block; align: center;",
                     uiOutput('ExposureTypeFilterSettingHist1UI'),
           br(),
           actionButton("selectAllCorporates", "Select All"),
           actionButton("deselectAllCorporates", "Deselect All")
       ))
       ,
    
      column(4,offset=2,
       div(style = "padding: 0px 0px; margin-left:0.1%",
          uiOutput('ExposureTypeFilterSettingHist2UI'),
           br(),
           actionButton("selectAllRetail", "Select All"),
           actionButton("deselectAllRetail", "Deselect All")
       ))
  )
  ,
    circle = F, status = "primary", width = "400px",
    tooltip = tooltipOptions(title = "Click to modify")
  ))),
   tabPanel(
                   div(style="display: inline-block; align: center;",
                       shinyWidgets::dropdown(label='Portfolio', status = "primary",
      fluidRow(
         column(10,offset=0,
            div(style = "padding: 0px 0px; margin-left:0.1%",
  radioGroupButtons(inputId = "PortfolioTypeSelection", individual = T,
   choices = c("IRB","SA","IRB and SA"), selected = 'IRB',
    checkIcon = list(yes = tags$i(class = "fa fa-circle", 
      style = "color: steelblue"), 
      no = tags$i(class = "fa fa-circle-o", 
        style = "color: steelblue")))
    ))))
    ,
      circle = F, status = "primary",
      icon = icon("time"), width = "300px",
      tooltip = tooltipOptions(title = "Click to modify inputs")
  )) ,tabPanel(
                   div(style="display: inline-block; align: center;",
                       shinyWidgets::dropdown(label='Portfolio Level', status = "primary",
      fluidRow(
         column(10,offset=0,
            div(style = "padding: 0px 0px; margin-left:0.1%",
  radioGroupButtons(inputId = "BreakDownMeasureFilterSettingHist", individual = T,
    label = "Portfolio Level Measures Selection", choices = colnames(CRE_Hist)[9:22], selected = 'EAD',
    checkIcon = list(yes = tags$i(class = "fa fa-circle", 
      style = "color: steelblue"), 
      no = tags$i(class = "fa fa-circle-o", 
        style = "color: steelblue")))
    ))))
    ,
      circle = F, status = "primary",
      icon = icon("time"), width = "300px",
      tooltip = tooltipOptions(title = "Click to modify inputs")
  )) ,tabPanel(
                   div(style="display: inline-block; align: center;",
                       shinyWidgets::dropdown(label='Bank Level', status = "primary",
      fluidRow(
         column(10,offset=0,
            div(style = "padding: 0px 0px; margin-left:0.1%",
  radioGroupButtons(inputId = "BankLevelFilterSettingHist", individual = T,
    label = "Bank Level Measure Setting", choices = colnames(CAPL_Hist)[4:33], selected = 'COMMON EQUITY TIER 1 CAPITAL RATIO (transitional period)',
    checkIcon = list(yes = tags$i(class = "fa fa-circle", 
      style = "color: steelblue"), 
      no = tags$i(class = "fa fa-circle-o", 
        style = "color: steelblue")))
    ))))
    ,
      circle = F, status = "primary",
      icon = icon("time"), width = "300px",
      tooltip = tooltipOptions(title = "Click to modify inputs")
  )) 
)
, 
HTML("<script>var parent = document.getElementsByClassName('navbar-nav');
parent[0].insertAdjacentHTML( 'afterend', '<ul class=\"nav navbar-nav navbar-right\"><li class=\"disabled\"><a href=\"#\">v0.1</a></li></ul>' );</script>")
    ))

```

```{r, include = FALSE}
outputOptions(x = output, name = "countryFilterSettingHist1UI", suspendWhenHidden = FALSE)
outputOptions(x = output, name = "countryFilterSettingHist2UI", suspendWhenHidden = FALSE)
outputOptions(x = output, name = "countryFilterSettingHist3UI", suspendWhenHidden = FALSE)
outputOptions(x = output, name = "countryFilterSettingHist4UI", suspendWhenHidden = FALSE)
outputOptions(x = output, name = "ExposureTypeFilterSettingHist1UI", suspendWhenHidden = FALSE)
outputOptions(x = output, name = "ExposureTypeFilterSettingHist2UI", suspendWhenHidden = FALSE)
```

Row {data-height=80}
-------------------------------------
  
### <span style="color:`r valueBoxTextColor`"></span>

```{r}
renderValueBox({
  valueBox(tags$p(paste0('Country Selection: ', paste(as.vector(c(input$countryFilterSettingHist1, 
                                                       input$countryFilterSettingHist2, 
                                                       input$countryFilterSettingHist3, 
                                                       input$countryFilterSettingHist4)), collapse = " ")), style = "font-size: 50%;"))
})
```

### <span style="color:`r valueBoxTextColor`"></span>

```{r}
renderValueBox({
  valueBox(tags$p(paste0('Banks Selected: ', length(input$bankFilterSettingHist)), style = "font-size: 50%;"))
})
```

### <span style="color:`r valueBoxTextColor`"></span>

```{r}
renderValueBox({
  valueBox(tags$p(paste0('Portfolio Type: ', paste(input$PortfolioTypeSelection, collapse = " ")), style = "font-size: 50%;"))
})
```

### <span style="color:`r valueBoxTextColor`"></span>

```{r}
renderValueBox({
  valueBox(tags$p(paste('EAD Selection at', max(CRE_SubSelect()$CRE_HistSub$DateYQ), ':',round(sum(CRE_SubSelect()$CRE_HistSub[DateYQ==max(DateYQ),EAD])/1000), 'BN'), style = "font-size: 50%;"))
})
```

### <span style="color:`r valueBoxTextColor`"></span>

```{r}
renderValueBox({
  valueBox(tags$p('Source - EBA TR13/15:17, ST14/16', style = "font-size: 50%;"))
})
```

Row
-------------------------------------

### <span style="color:`r borderTextColor`">`r renderText(return(paste('Portfolio Level:', input$BreakDownMeasureFilterSettingHist)))`</span>
```{r}
CRE_ItemSelect <- reactive({
input$renewValue

CRE_temp <- CRE_SubSelect()$CRE_HistSub  
CRE_temp[, Selected := get(input$BreakDownMeasureFilterSettingHist)]
print(summary(CRE_temp$Selected))
if(!(input$BreakDownMeasureFilterSettingHist %in% colnames(CRE_Hist)[15:22])) CRE_temp[, Selected := Selected/1000]
print(summary(CRE_temp$Selected))

Selectedplot <- hchart(CRE_temp[!is.na(Selected) & is.finite(Selected) & Selected!=0], "line", 
                       hcaes(x = DateYQ, y = round(Selected,2), group = Repline))%>% 
  hc_yAxis(title=list(text='Coverage Ratio'),
           labels=list(format = ifelse(input$BreakDownMeasureFilterSettingHist %in% colnames(CRE_Hist)[15:22], '{value}%', '{value} BN')))%>% 
  hc_xAxis(title=list(text='Period'))%>%
  hc_add_theme(thm)  %>%
  hc_colors(CRE_temp[!is.na(Selected) & is.finite(Selected) & Selected!=0, unique(ReplineColor), by = Repline]$V1)  

return(list(Selectedplot = Selectedplot))
})


renderHighchart({
  input$renewValue
  CRE_ItemSelect()$Selectedplot
})
  
```

### <span style="color:`r borderTextColor`">`r renderText(return(paste('Bank Level Capital/P&L:', input$BankLevelFilterSettingHist)))`</span>

```{r}

PnL_Plot <- reactive({
CAPL_HistSub <- CAPL_Hist[BankNameShort %in% input$bankFilterSettingHist]
CAPL_HistSub[, Selected := get(input$BankLevelFilterSettingHist)]
if(!(input$BankLevelFilterSettingHist %in% colnames(CAPL_Hist)[27:33])) CAPL_HistSub[,Selected:=Selected/1000]
SelMeasBankLevplot <-  hchart(CAPL_HistSub[!is.na(Selected) & is.finite(Selected) & Selected!=0], "line", 
                              hcaes(x = DateYQ, y = round(Selected,2) , group = BankNameShort))%>% 
                              hc_yAxis(title=list(text=input$BankLevelFilterSettingHist),
                                       labels=list(format = ifelse(input$BankLevelFilterSettingHist %in% colnames(CAPL_Hist)[27:33], '{value}%', '{value} BN')))%>% 
                              hc_xAxis(tickInterval=.5)%>% 
                              hc_add_theme(thm) %>%
                              hc_colors(CAPL_HistSub[!is.na(Selected) & is.finite(Selected) & Selected!=0, unique(ColorBase), by = BankNameShort]$V1)   
#profits plotting
#CAPL_Hist[, ProfitDiff := shift(diff(`PROFIT OR (-) LOSS FOR THE YEAR`), places = 1), by = 'BankNameShort']
#CAPL_Hist[DateYQ %in% c(2014,2015), `PROFIT OR (-) LOSS FOR THE YEAR` := `PROFIT OR (-) LOSS FOR THE YEAR`/2] #'biannualize'
#CAPL_Hist[DateYQ %in% c(2016,2017), `PROFIT OR (-) LOSS FOR THE YEAR` := ProfitDiff] 
#
#Profitplot <-  hchart(CAPL_Hist, "line", hcaes(x = DateYQ, y = round(`PROFIT OR (-) LOSS FOR THE YEAR`,2) , group = BankNameShort))%>% 
#                      hc_add_theme(thm) %>%
#                      hc_xAxis(tickInterval=.5)%>% 
#                      hc_colors(lineColors[-1])   


return(list(SelMeasBankLevplot = SelMeasBankLevplot))
})
```

```{r}

renderHighchart({
  input$renewValue
  PnL_Plot()$SelMeasBankLevplot
})

```


Row
-------------------------------------

### <span style="color:`r borderTextColor`">Risk Weighting Visualisation for Portfolio Subselection</span>

```{r}
CRE_SubSelect <- reactive({
input$renewValue
# combine all country filter settings  
countryFilterSettingHist <- as.vector(c(input$countryFilterSettingHist1, input$countryFilterSettingHist2, input$countryFilterSettingHist3, input$countryFilterSettingHist4))
# combine all sector filter settings
ExposureTypeFilterSettingHist <- as.vector(c(input$ExposureTypeFilterSettingHist1, input$ExposureTypeFilterSettingHist2))
#Subselect historic credit risk data
if (input$PortfolioTypeSelection=="IRB and SA"){PortfolioType <- c('IRB','SA')} else { PortfolioType <- input$PortfolioTypeSelection}
CRE_HistSub <- CRE_Hist[Country %in% countryFilterSettingHist & ExposureLabel %in% ExposureTypeFilterSettingHist & 
                          BankNameShort %in% input$bankFilterSettingHist & Portfolio%in%PortfolioType, ]
CRE_HistSub[, Repline     := paste(BankNameShort,ExposureLabel,Country, Portfolio)]

setkey(CRE_HistSub, BankNameShort, DateYQ)

# differentiate base colors for replines within each bank
MapReplineColors <-unique(CRE_HistSub[,.(ColorBase,Repline)])
MapReplineColors[, ReplineColor := ColorPaletteGenerate(ColorBase, length(unique(Repline))),  by = ColorBase]
CRE_HistSub <- merge(CRE_HistSub, MapReplineColors[,.(Repline, ReplineColor)], by = 'Repline')


#Subselect scenario credit risk data
ST_CRE16Sub <- ST_CRE16[Country %in% countryFilterSettingHist & ExposureLabel %in% ExposureTypeFilterSettingHist & 
                          BankNameShort %in% input$bankFilterSettingHist & Portfolio%in%PortfolioType, ]
ST_CRE16Sub[, Repline := paste(BankNameShort,ExposureLabel,Country,Portfolio,Scenario)]
setkey(ST_CRE16Sub, Scenario, Portfolio,BankNameShort, DateYQ)
#assign colors by scenario

# differentiate base colors for replines within each bank
MapReplineColors <-unique(ST_CRE16Sub[,.(ColorBase,Repline, Scenario)])
MapReplineColors[Scenario=='Adverse', ReplineColor := ColorPaletteGenerate(ColorBase, length(unique(Repline)), Scenario = 'Adverse'),  by = ColorBase]
MapReplineColors[Scenario=='Baseline', ReplineColor := ColorPaletteGenerate(ColorBase, length(unique(Repline)), Scenario = 'Baseline'),  by = ColorBase]
ST_CRE16Sub <- merge(ST_CRE16Sub, MapReplineColors[,.(Repline, ReplineColor)], by = 'Repline')
# mergeCol <- unique(ST_CRE16Sub[,.(Scenario, Repline)])
# mergeCol[Scenario=='Adverse', ReplineCol := brewer.pal(length(unique(ST_CRE16Sub$Repline))/2, 'Blues')]
# mergeCol[Scenario=='Baseline', ReplineCol := brewer.pal(length(unique(ST_CRE16Sub$Repline))/2, 'Oranges')]
# ST_CRE16Sub <- merge(ST_CRE16Sub, mergeCol[,.(Repline, ReplineCol)], by = 'Repline')

hchart(CRE_HistSub[!is.na(`Risk Weights`) & is.finite(`Risk Weights`)], "line", hcaes(x = DateYQ, y = round(`Risk Weights`,2), group = Repline))%>%
   hc_yAxis(title=list(text='Risk weight'),labels=list(format = '{value}%')) %>%
   hc_xAxis(title=list(text='Period'))%>%
   hc_add_theme(thm) %>%
   hc_colors(CRE_HistSub[!is.na(`Risk Weights`) & is.finite(`Risk Weights`), unique(ReplineColor), by = Repline]$V1) 


return(list(CRE_HistSub = CRE_HistSub, ST_CRE16Sub = ST_CRE16Sub))
})
```

```{r}

renderHighchart({
 hchart(CRE_SubSelect()$CRE_HistSub[!is.na(`Risk Weights`) & is.finite(`Risk Weights`)], "line", hcaes(x = DateYQ, y = round(`Risk Weights`,2), group = Repline))%>%
   hc_yAxis(title=list(text='Risk weight'),labels=list(format = '{value}%')) %>%
   hc_xAxis(title=list(text='Period'))%>%
   hc_add_theme(thm) %>%
   hc_colors(CRE_SubSelect()$CRE_HistSub[!is.na(`Risk Weights`) & is.finite(`Risk Weights`), unique(ReplineColor), by = Repline]$V1) 
})
  
```

### <span style="color:`r borderTextColor`">Coverage Ratio for Portfolio Subselection</span>

```{r}
renderHighchart({
  hchart(CRE_SubSelect()$CRE_HistSub[!is.na(`Coverage Ratio`) & is.finite(`Coverage Ratio`)],
         "line", hcaes(x = DateYQ, y = round(`Coverage Ratio`,2), group = Repline))%>% 
  hc_yAxis(title=list(text='Coverage Ratio'),labels=list(format = '{value}%'))%>% 
  hc_xAxis(title=list(text='Period'))%>%
  hc_add_theme(thm) %>%
  hc_colors(CRE_SubSelect()$CRE_HistSub[!is.na(`Coverage Ratio`) & is.finite(`Coverage Ratio`), unique(ReplineColor), by = Repline]$V1) 
})

```

### <span style="color:`r borderTextColor`">Projected Impairment Rates in % for Portfolio Subselection</span>
```{r}
renderHighchart({
  input$renewValue
  hchart(CRE_SubSelect()$ST_CRE16Sub[!is.na(ImpairmentRate) & is.finite(ImpairmentRate)], showInLegend = T, 
       "line", hcaes(x = DateYQ, y = round(ImpairmentRate * 100,2), group = Repline))%>%
  hc_yAxis(title=list(text='Impairment Rate'),labels=list(format = '{value}%')) %>%
  hc_xAxis(title=list(text='Period'),tickInterval=1)%>%
  hc_add_theme(thm)%>%
  hc_colors(unique(CRE_SubSelect()$ST_CRE16Sub[!is.na(ImpairmentRate) & is.finite(ImpairmentRate)]$ReplineColor))
  
  # hc_add_series(data = NULL, name = 'Baseline',  color = 'rgb(16, 124, 41)', showInLegend = T)%>%
  # hc_add_series(data = NULL, name = 'Adverse',  color = 'rgb(224, 24, 24)', showInLegend = T)%>%
  # hc_colors(c('rgb(224, 24, 24)','rgb(16, 124, 41)'))
  
  # hchart(CRE_SubSelect()$ST_CRE16Sub[!is.na(ImpairmentRate) & is.finite(ImpairmentRate)], showInLegend = F, 
  #        "line", hcaes(x = DateYQ, y = round(ImpairmentRate * 100,2), group = Repline))%>%
  # hc_yAxis(title=list(text='Impairment Rate'),labels=list(format = '{value}%')) %>%
  # hc_xAxis(title=list(text='Period'),tickInterval=1)%>%
  # hc_add_theme(thm) %>%
  # hc_add_series(data = NULL, name = 'Baseline',  color = 'rgb(16, 124, 41)', showInLegend = T)%>%
  # hc_add_series(data = NULL, name = 'Adverse',  color = 'rgb(224, 24, 24)', showInLegend = T)#%>%
  # hc_colors(c('rgb(16, 124, 41)', 'rgb(224, 24, 24)')) 
})
  
```




